---
title: "Knitting Club"
subtitle: "What is R Markdown and why do you need it?"
author: "Matt Dray"
date: "Coffee & Coding, 7 April 2018"
output:
  ioslides_presentation:
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, error = FALSE)
library(leaflet)
library(dplyr)
```

## TL;DR

## Why?

## Process

1. Open a file with the .Rmd (<u>R</u> <u>M</u>ark<u>d</u>own) extension
2. Write your report using R Markdown
3. Embed code that calculates values or produces plots and tables, for example
4. Use the `knitr` package to *knit* the document, rendering your R Markdown into a 'proper' document for sharing

## Open

File > New File > R Markdown

## Write

Plain text that's been 'marked-up'

## Output

YAML

# code

## inline

## chunks

````
```{r quake-map}`r ''`
library(leaflet)
library(dplyr)

quakes %>%
  dplyr::slice(1:10) %>%
  leaflet::leaflet() %>%
  leaflet::addProviderTiles(providers$OpenStreetMap) %>%
  leaflet::addMarkers(popup = ~paste("Magnitude", mag))
```
````

## chunks

```{r}
quakes %>% 
  dplyr::slice(1:10) %>%
  leaflet::leaflet() %>%
  leaflet::addProviderTiles(providers$OpenStreetMap) %>% 
  leaflet::addMarkers(popup = ~paste("Magnitude", mag))
```

## chunks

```{r echo=TRUE}
iris %>%
  dplyr::select(Species, Petal.Length, Sepal.Length) %>% 
  dplyr::slice(1:5)
```

## Render

Hit 'knit'

## More

RMarkdown long form document published on [RPubs](https://rpubs.com/mattdray/knitting-club) and [GitHub](https://github.com/matt-dray/knitting-club)